Binarity's Biases on Transit Survey Occurrence Rates

### 2018-02-23 paper/main.tex
jnw results edits

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{ {\it Top.}---Volumes within which sources appear to be
      searchable for planets of radius $r$.  Single stars are
      searchable out to a distance $d_0$, at which point they become
      too faint to allow the detection of transits.  Binaries
      are brighter and therefore appear to be searchable out to a
      larger distance.  {\it Bottom.}---Volumes within which within
      which stars appear to be searchable for planets of radius
      $r/\sqrt{2}$.  }
    \label{fig:model_1_volumes}
\end{figure}

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{ Apparent occurrence rate $\Lambda\a$, and true
    occurrence rate $\Lambda$ in a universe with only one type of
    star, one type of planet (with radius $R_\oplus$), and a number
    density of binary stars 5\% that of single stars.  The occurrence
    rate of planets with radius $R_\oplus$ is underestimated, and the
    occurrence rate of planets with radius
    $R_\oplus/\sqrt{2}$ is overestimated.}
    \label{fig:occ_rate_model_1}
\end{figure}

We can now assess the severity of the errors, for a given value of the
binary-to-single ratio $n\b/n\s$. For stars with masses from 0.7 to
1.3~$M_\odot$, \citet{raghavan_survey_2010} found the multiplicity
fraction~--~the fraction of systems in a volume-limited sample that
are multiple~--~to be 0.44.  Assuming all multiple systems are
binaries, this gives a binary fraction
\begin{equation}
  \frac{n\b}{n\s + n\b} \approx 0.44,
\end{equation}
which implies $n\b/n\s \approx 0.79$.  Of course not all of
these binaries are ``twin'' binaries as we have assumed in our simple
calculation.  Later, in Section~\ref{sec:general_formula}, we will
allow for a continuum of properties for the secondary stars. For now,
we might guess that only a tenth of the binaries have pairs of stars
close enough in brightness to produce errors as significant as those
we have been considering.  Adopting the value $n\b/n\s\approx0.05$, we
find
\begin{equation}
    \frac{\Lambda\a(r\p)}{\Lambda(r\p)} = 0.88,~~
    \frac{\Lambda\a(r\p/\sqrt{2})}{\Lambda(r\p)} = 0.25.
    \label{eq:ratios}
\end{equation}
All together, the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is
characteristic of many of our more complicated models as well.

\subsection{Formula Based on Apparent Rate Density}
\label{sec:model_1_density}

There is a different way to conceptualize the preceding results that
will be useful in the upcoming discussion. We now consider a spectrum
of planet sizes, $r$, and introduce the occurrence rate density
\begin{equation}
    \Gamma(r) \equiv \frac{{\rm d}\Lambda}{{\rm d}r},
    \label{eq:rate_density_defn}
\end{equation}
the number of planets per star per unit planet radius.

The naive observers are in fact measuring $\Gamma\a(r\a)$, the {\it
apparent} occurrence rate density~--~the number of planets per star
per unit apparent radius $r\a$.  The ``apparent planet radius'' is the
radius inferred from the transit depth under the assumption that the
host star is single. The ``apparent stellar radius'' $R\a$ is
analogous.  The observed transit depth can be written $\delta =
(r\a/R\a)^2$, which from Equation~\ref{eq:delta_obs_general} gives
$r\a=r\p/\sqrt{2}$ for planets in twin binaries.  $\Gamma\a(r\a)$ is
the same as the {\it true} rate density of transit signals of
amplitude $\delta$.

We will now calculate the apparent rate density by evaluating the star
and planet counts for signals coming from single stars, primary stars
in binaries, and secondary stars in binaries.  Let $\mu$ be the ratio
between the number of searchable binary systems and the number of
searchable single systems at a particular transit depth. The number of
single and binary sources in the searched sample are then
\begin{equation}
  \frac{N_\star(r\a)}{1+\mu}~~{\rm and}~~\frac{\mu N_\star(r\a)}{1+\mu},
  \label{eq:N_searched}
\end{equation}
respectively.  Earlier we showed that due to Malmquist bias, $\mu =
2^{3/2}(n\b/n\s)$.

Suppose the occurrence rate densities for planets around
single stars, primaries, and secondaries are $\Gamma_0(r),
\Gamma_1(r)$, and $\Gamma_2(r)$, respectively. For a single planet
size,
\begin{equation}
    \Gamma_i(r) = \Lambda(r\p) \, \hat{\delta}(r-r\p),~~{\rm for}
    \ i\in\{0,1,2\},
    \label{eq:one_planet}
\end{equation} 
where $\hat{\delta}$ is the Dirac delta function.
The number of planets detected from singles, primaries, and
secondaries are then
\begin{align}
  n_{\rm det}^0(r\a)\mathrm{d}r\a &= 
      \frac{N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_0(r\a)\mathrm{d}r\a,
  \label{eq:n0} \\
  n_{\rm det}^1(r\a)\mathrm{d}r\a &= 
      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n1} \\
  n_{\rm det}^2(r\a)\mathrm{d}r\a &=
      \frac{\mu N_\star(r\a)}{1+\mu} p_{\rm tra}
      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n2}
\end{align}
where $n_{\rm det}^i$ is the number of detections per unit apparent
radius for each respective type of star.

Dividing the number of detections by the number of sources,
the apparent rate density reported when ignoring binarity is
\begin{equation}
  \Gamma\a(r\a) =
    \frac{1}{1+\mu}\,\Gamma_0(r\a) +
    \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_1(\sqrt{2}r\a) +
    \frac{\mu}{1+\mu}\,\sqrt{2}\,\Gamma_2(\sqrt{2}r\a).
	\label{eq:formula_twin_binary}
\end{equation}
If we insert Equation~\ref{eq:one_planet} and integrate over
apparent radius, this reproduces Equations~\ref{eq:rate_at_rp}
and~\ref{eq:correction_diluted_rp}.

\begin{comment}
  and inputting Equation~\ref{eq:one_planet}, we find
  \begin{align}
      \Gamma\a(r\a) &= \Lambda(r\p) \left[
      \frac{1}{1+\mu} \cdot
      \hat{\delta}(r\a-r\p)  +
      \frac{2\mu}{1+\mu} \cdot
      \delta\left(r\a-\frac{r\p}{\sqrt{2}} \right) \right].
      \label{eq:model_1_apparent_rate_density}
  \end{align}
  Integrating over $r\a$, this yields
  \begin{equation}
    \Lambda\a(r_{\rm p})=\frac{Z}{1+\mu},\quad
    \Lambda\a(r_{\rm p}/\sqrt{2})=\frac{2\mu Z}{1+\mu},
  \end{equation}
  which reproduce Equations~\ref{eq:correction_rp}
  and~\ref{eq:correction_diluted_rp}.
\end{comment}

\begin{comment}
    The ratio of the apparent to single star rate
    densities,
    \begin{equation}
        X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)}
          \right|_{r\a = r},
    \end{equation}
    can then be evaluated as a ``correction factor''.  At the true and
    diluted planet radii, $X_\Gamma(r\p)=1/(1+\mu)$ and
    $X_\Gamma(r\p/\sqrt{2})=2\mu/(1+\mu)$.  This yields a correction
    $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 0.05~(0.10).
    All together the various effects produce biases of order 10\% in the
    occurrence rates.  
\end{comment}

\begin{comment}
    \subsection{One type of star, two types of planets}

    A simple extension to the previous example helps distinguish between
    the apparent and underlying planet populations.  Consider now a
    universe that is the same as in Section~\ref{sec:model_1}, except that
    half of planets have radii $r\p$, while the other half have radii
    $r\p/\sqrt{2}$.  The rate densities are
    \begin{equation}
        \Gamma_i(r) = \frac{Z_i}{2} \left[
        \hat{\delta}(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
        \right], \quad {\rm for}\  i \in \{ 0,1,2 \},
    \end{equation}
    where $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to
    secondaries, and the $Z_i$'s are the number of planets per star of
    each type.

    Following an identical line of reasoning as in
    Section~\ref{sec:model_1}, the apparent rate density can be written
    \begin{align}
        \notag
        \Gamma\a(r\a) &=
        \frac{1}{2(1+\mu)} \left[
        Z_0 \cdot \hat{\delta}(r\a - r\p)
        +
        \left[Z_0 + \mu (Z_1 + Z_2)
        \right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
        \right. \\
        &\quad\quad\quad\quad\quad\quad\quad\quad+
        \left.
        \mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
        \right].
        \label{eq:two_radii_twins}
    \end{align}
    Just as in Equation~\ref{eq:model_1_apparent_rate_density}, the
    $N_\star^0(r\a)$ terms cancel, leaving only the $\mu$ weights.
    However, there are now three detected planet sizes.  Also different is
    that two populations contribute at $r\a = r\p/\sqrt{2}$: the first
    population is singles with $r=r\p/\sqrt{2}$, and the second is twin
    binaries with $r=r\p$.  Both populations are detected out to the same
    maximum searchable distance.  More generally, at any given apparent
    radius, there will be contributions from both singles, primaries, and
    secondaries~---~but the relative weights between these contributions
    will depend on the underlying occurrence rates.
\end{comment}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{General formula for apparent occurrence rate}
\label{sec:general_formula}

To generalize the procedure of Section~\ref{sec:model_1_density} for
binaries with varying light ratios, we consider an SNR-limited survey
in which stars can have arbitrary properties.  We assume that there
are some functions $L(M)$ and $R(M)$ that specify a star's luminosity
and radius in terms of its mass. We also presume that the observers
know the masses of every single and primary star, and that they assign
each binary system the properties of its primary.  Finally, we take
the volume-limited distribution of binary mass ratios, $f(q)$, to be
independent of the primary star's mass.

We want an equation for $\Gamma\a(r\a,M\a)$, the apparent rate density
at each apparent planet radius and apparent stellar mass\footnote{By
assumption, the apparent stellar mass for single star systems is the
true mass. For binary systems, the apparent mass is the mass of the
primary.}.
Similar to Equation~\ref{eq:rate_density_defn}, we define
$\Gamma(r,M)$ as the number of planets per star, per unit planet radius,
per unit stellar mass.  Due to the varying binary mass ratios, we need
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different. The ratio between the number of
binary and single systems for which a transit of depth $\delta$ is
detectable, $\mu$, has changed.  At any $(r\a,M\a)$ pair, the number
of binary systems in the searchable volume with mass ratio $(q,
q+\mathrm{d}q)$ is now
\begin{equation}
    {N_\star(r\a)\over{1+\mu}} \, {n_{\rm b}\over n_{\rm s}}
    \left[{L_{\rm tot}(M\a, q) \over L(M\a)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L_{\rm tot}(M\a, q)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
Binaries with larger mass ratios are overrepresented by a factor of
$\left[{L_{\rm tot}(M\a, q)/L(M\a)}\right]^{3/2}$ because the
sample of searchable binaries is magnitude-limited.  To obtain
the number of binary systems searched at each $(r\a,M\a)$ pair,
Equation~\ref{eq:N_binaries} needs to be integrated over $q$.  It
can then replace ${\mu N_\star(r\a)/(1+\mu)}$ in
Equations~\ref{eq:n1} and~\ref{eq:n2}.

\item The apparent radius of a planet in a binary system now depends
on whether the host star is the primary or the secondary. When the host
is the primary, we write
$r=\mathcal{D}_1 r\a$, where
\begin{equation}
    \mathcal{D}_1
    = \left( \frac{ L_{\rm tot}(M\a, q)}{ L(M\a) } \right)^{1/2}.
    \label{eq:dil_1}
\end{equation}
When the host is the secondary, $r=\mathcal{D}_2 r\a$, and the
ratio between the assumed and true stellar radii must be included:
\begin{equation}
  \mathcal{D}_2
  = \frac{R(qM\a)}{R(M\a)}
    \left( \frac{L_{\rm tot}(M\a, q)}{L(qM\a)} \right)^{1/2}.
  \label{eq:dil_2}
\end{equation}

\item Since the observers assign binaries the properties of the
primary, the transit probability for planets orbiting secondaries is
over-estimated. At a fixed orbital period, this changes
$p_{\rm tra}$ in Equation~\ref{eq:n2} by a factor of
\begin{equation}
  {R(qM\a) \over R(M\a)}q^{-1/3}.
\end{equation}

\item The contribution to the apparent rate density from
secondaries now depends on the mass of the secondary, $qM\a$. The
associated measure on the right-hand side of
Equation~\ref{eq:n2} becomes ${\rm d}(qM\a)$, and gives rise to an
extra multiplicative factor of $q$.

@@

Taking these modifications into account, a general formula for the
apparent rate density follows:
\begin{align}
    \notag
    \Gamma\a(r\a,M\a) &= \frac{1}{1+\mu}
    \left\{ \Gamma_0(r\a, M\a)+ 
    \frac{n\b}{n\s}
    \left[ \int_0^1 \mathrm{d}q \,
           \mathcal{D}_1^3 f(q)\cdot
           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a, M\a)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \mathcal{D}_1^3 f(q)\cdot q \mathcal{D}_2
         \Gamma_2(\mathcal{D}_2r\a, qM\a)\cdot
         \frac{R(qM\a)}{R(M\a)} q^{-1/3}
    \right] \right\}.
    \label{eq:general_Gamma_a}
\end{align}
We give an alternative derivation in the
\hyperref[sec:appendix]{Appendix}.
With the definition of $\mu$ in Equation~\ref{eq:mu_general},
Equation~\ref{eq:general_Gamma_a} can also be expressed as
\begin{align}
    \notag
    \notag
    \Gamma\a(r\a,M\a)
    &= 
    {1\over 1+\mu}
    \left[
       \Gamma_0(r\a, M\a) \phantom{\frac{1}{1}}
       \right.&\\
       &\quad\quad \left.+\mu
       \left\langle
       \mathcal{D}_1\Gamma_1\left(\mathcal{D}_1r\a, M\a\right)
       +
       {q \mathcal{D}_2}\Gamma_2\left(\mathcal{D}_2r\a,
       qM\a\right) \cdot {R(qM\a) \over R(M\a)}q^{-1/3}
       \right\rangle
    \right],
\end{align}
where the angle brackets denote averaging over $\mathcal{D}_1^3f(q)$.
Summarized, the apparent rate density is a weighted sum of the rate
densities from singles, primaries, and secondaries.  The weights are
determined by the fraction $\mu$ and mass ratio distribution
$\mathcal{D}_1^3f(q)$ of binaries {\it in the searchable volume}.  The
fraction $\mu$ gives the relative contributions from singles and
binaries, and $\mathcal{D}_1^3 f(q)$ applies a Malmquist bias for
binaries that are brighter.  A final correction for secondaries
accounts for the overestimated transit probability.

@@

\section{Realistic Star and Planet Distributions}
\label{sec:more_complicated}

We will now apply our general equation for the apparent rate density
(Equation~\ref{eq:general_Gamma_a}) to study the impact of
unrecognized binaries in regimes of observational interest.  In the
following, we write the rate density for each type of star,
$\Gamma_i(r)$, as the product of a shape function, normalized to
unity, and a constant:
\begin{equation}
    \Gamma_i(r) = Z_i f_i(r), \quad {\rm for\ }i\in\{0,1,2\},
\end{equation}
where the respective indices correspond to single stars, primaries of
binaries, and secondaries of binaries.  The normalizations $Z_i$ are
each system type's occurrence rate $\Lambda_i$, integrated over all
planetary radii. In other words, they are number of planets per
single, primary, or secondary star.  Our main interest is in
varying the radius shape function and the relative values of the
integrated occurrence rates. We will also briefly mention shape
functions in stellar mass.  For analytic simplicity, we will assume
throughout this section that stars are a one-parameter family, given
by $L \propto M^\alpha \propto R^\alpha$.  Applying these power laws
to Equations~\ref{eq:dil_1} and~\ref{eq:dil_2}, we find
\begin{equation}
  \mathcal{D}_1
  =  (1+q^\alpha)^{1/2}~~{\rm and}~~\mathcal{D}_2
  = q(1+q^{-\alpha})^{1/2}
\end{equation}
for the radius dilution prefactors.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Power law planet radius distribution}
\label{sec:model_2}

\subsubsection{Twin binaries}
As a first step, we return to the case where all binaries are twins.
However, we now let the planet radius distribution be a power law,
\begin{equation}
    \Gamma_i(r) = Z_i f(r) = Z_i r^\gamma/\mathcal{N}_r,
\end{equation}
for $\mathcal{N}_r$ the shape function's normalization.  Applying
Equation~\ref{eq:general_Gamma_a} gives the resulting apparent rate
density,
\begin{equation}
    \Gamma\a(r\a) = \frac{r\a^{\gamma}}{\mathcal{N}_r} \left[
    \frac{Z_0}{1+\mu}
    +
    2^{\frac{\gamma+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2
    \right)
    \right].
    \label{eq:model5_apparent_rate_density}
\end{equation}
Under these assumptions, twin binaries simply shift the apparent
radius distribution: $\Gamma\a(r\a) \propto r\a^\gamma$.  As in
Section~\ref{sec:model_1}, $\mu = 2^{3/2} n\b/n\s$.  If planet
occurrence is independent of system multiplicity, the ``correction
factor'' relative to the rate density for singles is
\begin{align}
    \frac{\left. \Gamma\a(r\a)\right|_{r\a= r}}{\Gamma_0(r)} 
    &=
    \frac{1 + 2^{\frac{\gamma+3}{2}}\mu}{1 + \mu}.
    \label{eq:power_law_correction}
\end{align}
For a binary fraction of $0.1$, $\mu\approx 0.15$. Taking
$\gamma=-2.92$ from \citet{howard_planet_2012},  we find that the
apparent rate density is a mere 0.4\% larger than the rate density of
single stars.  Fortuitously, the exponent of the radius distribution
is close to $-3$, and the errors from neglecting binaries almost
entirely cancel out.

>>>>

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=0.6\textwidth]{figures/visualize_volumes.pdf}
    \end{center}
    \caption{ {\it Top.}---Volumes within which sources appear to be
      searchable for planets of radius $r$.  Single stars are
      searchable out to a distance $d_0$, at which point they become
      too faint to allow the detection of transits.  Binaries
      are brighter and therefore appear to be searchable out to a
      larger distance.  {\it Bottom.}---Volumes within
      which stars appear to be searchable for planets of radius
      $r/\sqrt{2}$.  }
    \label{fig:model_1_volumes}
\end{figure}

\begin{figure}[!tb]
    \begin{center}
        \includegraphics[width=.6\textwidth]{figures/occ_rate_vs_radius_model_1_brokenx.pdf}
    \end{center}
    \vspace{-0.5cm}
    \caption{ Apparent occurrence rate $\Lambda\a$, and true
    occurrence rate $\Lambda$ in a universe with only one type of
    star, one type of planet (with radius $R_\oplus$), and a number
    density of binary stars 5\% the number density of single stars.
    The occurrence
    rate of planets with radius $R_\oplus$ is underestimated, and the
    occurrence rate of planets with radius
    $R_\oplus/\sqrt{2}$ is overestimated.}
    \label{fig:occ_rate_model_1}
\end{figure}

We can now assess the severity of the errors, for a given value of the
binary-to-single ratio $n\b/n\s$. For stars with masses from 0.7 to
1.3~$M_\odot$, \citet{raghavan_survey_2010} found the multiplicity
fraction~--~the fraction of systems in a volume-limited sample that
are multiple~--~to be 0.44.  Assuming all multiple systems are
binaries, this gives a binary fraction
\begin{equation}
  \frac{n\b}{n\s + n\b} \approx 0.44,
\end{equation}
which implies $n\b/n\s \approx 0.79$.  Of course not all of
these binaries are ``twin'' binaries as we have assumed in our simple
calculation.  Later, in Section~\ref{sec:general_formula}, we will
allow for a continuum of properties for the secondary stars. For now,
we might guess that only a tenth of the binaries have pairs of stars
close enough in brightness to produce errors as significant as those
we have been considering.  Adopting the value $n\b/n\s\approx0.05$, we
find
\begin{equation}
    \frac{\Lambda\a(r)}{\Lambda(r)} = 0.88,~~
    \frac{\Lambda\a(r/\sqrt{2})}{\Lambda(r)} = 0.25.
    \label{eq:ratios}
\end{equation}
All together, the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is
characteristic of many of our more complicated models as well.

\subsection{Planets of different sizes}
\label{sec:model_1_density}

We will now generalize to allow for a continuum of planet sizes.   We
introduce the occurrence rate density
\begin{equation}
    \Gamma(r) \equiv \frac{{\rm d}\Lambda}{{\rm d}r},
    \label{eq:rate_density_defn}
\end{equation}
the number of planets per star per unit planet radius.  The naive
observers are measuring $\Gamma\a(r\a)$, the apparent occurrence rate
density of planets with an ``apparent radius''
\begin{equation}
  r\a = R \sqrt{\delta}.
\end{equation}

For a given value of $r\a$, the observers assemble the sample of
$N_\star(r\a)$ sources for which a signal of amplitude $\delta =
(r\a/R)^2$ could have been detected.  We showed in the previous
section that when all stars are identical, this sample will contain
binaries and single stars in the ratio $2^{3/2}(n\b/n\s)$.  Here we
will denote this ratio by $\mu$, which will be calculated later in a
more general context.  With this definition, the number of single
stars is proportional to $1/(1+\mu)$ and the number of binaries is
proportional to $\mu/(1+\mu)$.

From within this sample of apparently searchable sources, the
observers sum the number of detections $dN_{\rm det}$ of planets
with an apparent radius between $r\a$ and $r\a + dr\a$.  There will be
three contributions to this sum,
\begin{align}
  dN_{{\rm det},0} &= 
      \frac{N_\star(r\a) p_{\rm tra}}{1+\mu}
      \Gamma_0(r\a)\mathrm{d}r\a,
  \label{eq:n0} \\
  dN_{{\rm det},1} &= 
      \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
      \Gamma_1(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a),
	\label{eq:n1} \\
  dN_{{\rm det},2} &=
      \frac{\mu N_\star(r\a) p_{\rm tra}}{1+\mu} 
      \Gamma_2(\sqrt{2}r\a)\mathrm{d}(\sqrt{2}r\a).
	\label{eq:n2}
\end{align}
where here and elsewhere, the subscript 0 refers to single stars, 1
refers to primary stars of binaries, and 2 refers to secondary stars
of binaries. The apparent occurrence rate density is therefore
\begin{equation}
  \Gamma\a(r\a) = \frac{dN_{\rm det}}{dr\a} \frac{1}{N_\star(r\a) p_{\rm tra}} =
  \frac{\Gamma_0(r\a)}{1+\mu} +
  \frac{\mu\sqrt{2}\,\Gamma_1(\sqrt{2}r\a)}{1+\mu} +
  \frac{\mu\sqrt{2}\,\Gamma_2(\sqrt{2}r\a)}{1+\mu}.
	\label{eq:formula_twin_binary}
\end{equation}
Our earlier results, Equations~\ref{eq:rate_at_rp}
and~\ref{eq:correction_diluted_rp}, are recovered by integrating this formula
over $r$ after inserting
\begin{equation}
  \Gamma_i(r) = \Lambda(r\p)\, \hat{\delta}(r-r\p),~~{\rm for}\ i\in\{0,1,2\}
\end{equation}
where $\hat{\delta}$ is the Dirac delta function, and $r\p$ is the
single planet size considered in Section~\ref{sec:model_1}.

\subsection{Binaries with different mass ratios}
\label{sec:general_formula}

Next we generalize to allow for a spectrum of different properties for
the secondary stars.  For simplicity we assume that the stars form a
one-parameter family specified by the stellar mass $M$.  This is
approximately the case for main-sequence stars.  The functions $L(M)$
and $R(M)$ give the luminosity and radius as a function of mass, and
$f(q)$ is the distribution of binary mass ratios in a volume-limited
sample.  We also assume that observers perceive all the binaries to be
isolated stars with the same mass as the primary star, i.e., the light
from the secondary star is either too faint or too similar to the
primary star to make a difference in the stellar classification.
Finally, for clarity of presentation we make the simplifying
assumption that $\Gamma_0$, $\Gamma_1$ and $\Gamma_2$ do not depend on
stellar mass, although our formalism can easily accommodate such a
dependence.

To compute the apparent occurrence rate density, we need to make
the following modifications to Equation~\ref{eq:formula_twin_binary}:
%
\begin{enumerate}
%
\item The Malmquist bias is different.  For a given value of $r\a$, the
  number of binary systems in the searchable sample with mass ratio
  $(q, q+\mathrm{d}q)$ is
\begin{equation}
    {N_\star(r\a)\over{1+\mu}}\cdot {n_{\rm b}\over n_{\rm s}}
    \left[{L(M) + L(qM) \over L(M)}\right]^{3/2}
    f(q)\,\mathrm{d}q,
    \label{eq:N_binaries}
\end{equation}
where $\mu$ is given by
\begin{equation}
    \mu= 
    %\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
    \int_0^1 {n_{\rm b}\over n_{\rm s}}\left[{L(M) + L(qM)
    \over L(M\a)}\right]^{3/2} f(q)\,\mathrm{d}q.
    \label{eq:mu_general}
\end{equation}
To obtain the total number of searchable binaries,
Equation~\ref{eq:N_binaries} needs to be integrated over $q$. The
result of the integration replaces ${\mu N_\star(r\a)/(1+\mu)}$ in
Equations~\ref{eq:n1} and~\ref{eq:n2}.

\item The apparent radius of a planet in a binary system now depends
on whether the host star is the primary or the secondary star. When the host
is the primary star, we write $r=\mathcal{D}_1 r\a$, where
\begin{equation}
    \mathcal{D}_1
    = \left[ \frac{ L(M) + L(qM) }{ L(M) } \right]^{1/2}
    \label{eq:dil_1}
\end{equation}
is the appropriate dilution factor.
When the host is the secondary star, a correction must also be made
to account for the different radius of the secondary star.
In that case $r=\mathcal{D}_2 r\a$, where
\begin{equation}
  \mathcal{D}_2
  = \frac{R(qM)}{R(M)}
    \left[ \frac{L(M) + L(qM)}{L(qM)} \right]^{1/2}.
  \label{eq:dil_2}
\end{equation}

\item When a transiting planet is detected around a secondary star,
  the naive observers make the wrong correction for the transit
  probability.  At a fixed orbital period, $p_{\rm tra}$
  in Equation~\ref{eq:n2} must be multiplied by a factor of
\begin{equation}
  {R(qM) \over R(M)}q^{-1/3}.
\end{equation}

@@

Taking these modifications into account, a general formula for the
apparent rate density is
\begin{align}
    \notag
    \Gamma\a(r\a) &= \frac{1}{1+\mu} \,
    \left\{ \Gamma_0(r\a)+ 
    \frac{n\b}{n\s}
    \left[ \int_0^1 \mathrm{d}q \,
           \mathcal{D}_1^3 f(q)\cdot
           \mathcal{D}_1 \Gamma_1(\mathcal{D}_1r\a)\,
    \right.   
    \right. \\
    & \quad\quad\quad\quad\quad \left.\left.
    +\int_0^1 {\rm d}q\, 
         \mathcal{D}_1^3 f(q)\cdot \mathcal{D}_2
         \Gamma_2(\mathcal{D}_2r\a)\cdot
         \frac{R(qM)}{R(M)} q^{-1/3}
    \right] \right\}.
    \label{eq:general_Gamma_a}
\end{align}
The \hyperref[sec:appendix]{appendix} gives an alternative derivation
of this equation.

We note that the combination $\mathcal{D}_1^3f(q)$ is the mass-ratio
distribution for binaries contained within the searchable sample of
sources.  With this in mind we may rewrite
Equation~\ref{eq:general_Gamma_a} as
\begin{align}
    %\notag
    %\notag
    \Gamma\a(r\a)
    =%&= 
    {1\over 1+\mu} \,
    \left[
       \Gamma_0(r\a)%\phantom{\tilde \Gamma}\right.%&\\
       %&\left.
       +\mu\,
       \left\langle
       \mathcal{D}_1\cdot\Gamma_1\left(\mathcal{D}_1r\a\right)
       +
       {q \mathcal{D}_2}\cdot\Gamma_2\left(\mathcal{D}_2r\a\right)
       \cdot
       {R(qM) \over R(M)}q^{-1/3}
       \right\rangle
    \right],
\end{align}
where the angle brackets denote averaging over all the binaries in the
searchable sample.

@@

\section{Case Studies}
\label{sec:more_complicated}

We can now gauge the size of the systematic errors associated
with unresolved binaries, for cases of interest.  Throughout this
section we assume $R\propto M$, and $L \propto M^{\alpha}$ where
$\alpha = 3.5$, as is roughly the case for main-sequence stars.
With these assumptions, Equations~\ref{eq:dil_1} and~\ref{eq:dil_2}
become
\begin{equation}
  \mathcal{D}_1
  =  (1+q^\alpha)^{1/2}~~{\rm and}~~\mathcal{D}_2
  = q(1+q^{-\alpha})^{1/2}.
\end{equation}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Power-law planet radius distribution}
\label{sec:model_2}

Based on {\it Kepler} data, \citet{howard_planet_2012} found the
radius distribution of planets between 2 and 17~$R_\oplus$ orbiting Sun-like
stars within 0.25\, AU to be consistent with a power law,
\begin{equation}
  \Gamma_0(r) \propto r^\gamma,
\label{eqn:power_law}
\end{equation}
with $\gamma=-2.92\pm 0.11$.  Their analysis ignored the effects of
binarity.  We can use our formalism to estimate the resulting level of
systematic error.

To warm up we will again consider the case in which all stars are
identical.  We assume further that the distributions of planets around
primaries and secondaries differ only by multiplicative factors,
\begin{equation}
    \Gamma_1 = Z_1 \Gamma_0,~~\Gamma_2 = Z_2 \Gamma_0.
\end{equation}
Application of Equation~\ref{eq:general_Gamma_a} gives
\begin{equation}
    \frac{\Gamma\a(r\a)}{\Gamma_0(r\a)} = 
    \frac{1}{1+\mu}
    +
    2^{\frac{\gamma+1}{2} } \frac{\mu}{1+\mu} \left(Z_1 + Z_2\right),
    \label{eq:model5_apparent_rate_density}
\end{equation}
where $\mu = 2^{3/2} n\b/n\s$.  The ratio does not depend on $r\a$ and
thus, under our assumptions, the effect of twin binaries is simply to
change the normalization of the radius distribution.  If we further
assume that planet occurrence is independent of system multiplicity,
i.e., $Z_1=Z_2=1$, then
\begin{equation}
    \frac{\Gamma\a(r\a)}{\Gamma_0(r\a)} = 
    \frac{1 + 2^{\frac{\gamma+3}{2}}\mu}{1 + \mu}.
    \label{eq:power_law_correction}
\end{equation}
Adopting $\gamma=-2.92$, and a twin binary fraction $n\b/n\s=0.05$, as
before, we obtain $\mu = 0.14$ and $\Gamma\a/\Gamma_0 = 1.003$.  The
correction is tiny because, by coincidence, the reported value of
$\gamma$ is very close to $-3$, the value for which
Equation~\ref{eq:power_law_correction} reduces to unity and the
effects of binarity cancel out completely.  This suggests that
although \citet{howard_planet_2012} derived the occurrence rate
density under the false assumption that all stars are single, the
resulting systematic error is negligible.

\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{ The mass ratio distribution of binaries in a
      magnitude-limited sample, assuming the underlying volume-limited
      distribution is uniform and the luminosity-mass relation is
      $L\propto M^{3.5}$. For transit signals of a given amplitude,
      the sample of searchable sources is magnitude-limited, causing
      high mass ratios to be over-represented. }
    \label{fig:q_distribn_mag_limited}
\end{figure}

For a more accurate analysis we now consider a distribution of binary
mass ratios.  Studies of binaries in the local neighborhood suggest
that the distribution of mass ratios is nearly uniform between zero
and unity~\citep{raghavan_survey_2010}.  We consider the more general
possibility of a power-law dependence, $f(q) = \mathcal{N}_q q^\beta$,
where $\mathcal{N}_q$ is a normalization constant.  In this case
Equation~\ref{eq:mu_general} gives
\begin{equation}
    \mu = \frac{1}{\mathcal{N}_q} \frac{n\b}{n\s}
    \int_0^1 (1+q^\alpha)^{3/2}q^\beta\,{\rm d}q.
    \label{eq:mu_power_law_q}
\end{equation}
Figure~\ref{fig:q_distribn_mag_limited} illustrates the Malmquist
bias for the particular case of a flat distribution.
